Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-13 analysis/Study1.qmd
changes rest of dimensions/ variable names

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
    ICQ = ICQ_sum,
    STAIT_Sum = STAIT_sum
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
```

@@

```{r}
df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation
  ) |>
  filter(!is.na(Urinate)) |> 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
```

@@

df13$PHQ4_Depression <- (df13$PHQ4_Depression_4 + df13$PHQ4_Depression_3)/2
df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2
```

@@

df16 <- read.csv("../data/Scharte2025/data_IAS_rs.csv") |>
  rename(Age= age, Gender = gender_identity, Education = education,
         Heart = ias1, Hungry = ias2, Breathing = ias3, Thirsty = ias4, Urinate = ias5, 
         Defecate=ias6, Taste = ias7,Vomit = ias8, Sneeze = ias9, Cough = ias10, 
         Temp = ias11, Sex_arousal = ias12, Wind = ias13, Burp = ias14,Muscles = ias15, 
         Bruise = ias16, Pain = ias17, Blood_Sugar = ias18, Affective_touch = ias19, 
         Tickle =ias20, Itch = ias21,
         GAD2_Sum = gad2,
         PHQ2_Sum = phq2
         ) |>
  mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 4, 5) ~ "Other",
    Gender == 6 ~ "NA"),
    Education = case_when(
      Education == 6 ~ "Bachelor",
      Education == 7 ~ "Master",
      Education == 8 ~ "Doctorate",
      Education == 2 | Education == 3 ~ "High School", # GCSE + A-levels (16-18 years old)
      Education == 4 | Education == 5 ~ "Other",       # NVQ and foundation year
      Education == 1 ~ "No education"),
    MAIA_Noticing = (maia1 + maia2 + maia3 + maia4)/4,
    MAIA_NotDistracting = (maia5_rev + maia6_rev + maia7_rev +maia8_rev + maia9_rev + maia10_rev)/6, 
    MAIA_NotWorrying = (maia11_rev +maia12_rev  + maia13)/3,
    MAIA_AttentionReg = (maia16 + maia17 + maia18 + maia19 + maia20 + maia21 + maia22)/7,
    MAIA_EmoAwareness = (maia23 + maia24 + maia25 + maia26 +maia27)/5,
    MAIA_SelfReg = (maia28 + maia29 + maia30 + maia31)/4,
    MAIA_BodyListening = (maia32 + maia33 +maia34)/3,
    MAIA_Trusting = (maia35 + maia36 + maia37)/3 ,
    GAD7_Sum = rowSums(across(starts_with("gad1_")), na.rm = TRUE),
    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE)) |>
  filter (!Age == 2004.00, !Age == 1999.00, # misreported age
          att == 2) # only those that select 'no' the attention check

>>>>

df7c <- haven::read_sav("../data/Brand2023/Data_PotVie.sav") |> 
  select(-ID) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(GENDER == 2, "Male", ifelse(GENDER == 1, "Female", "Other")))) |> 
  rename(
    Age=AGE, Heart = IA02_01, Hungry = IA02_02, Breathing = IA02_03, Thirsty = IA02_04,
    Urinate = IA02_05, Defecate = IA02_06, Taste = IA02_07, Vomit = IA02_08, Sneeze = IA02_09,
    Cough = IA02_10, Temp = IA02_11, Sex_arousal = IA02_12, Wind = IA02_13, Burp = IA02_14,
    Muscles = IA02_15, Bruise = IA02_16, Pain = IA02_17, Blood_Sugar = IA02_18,
    Affective_touch = IA02_19, Tickle = IA02_20, Itch = IA02_21,
    MAIA_Noticing = MAIA_noticing, MAIA_NotDistracting = MAIA_notdis, 
    MAIA_NotWorrying = MAIA_notwor, MAIA_AttentionReg = MAIA_attreg,
    MAIA_SelfReg = MAIA_selfreg, MAIA_BodyListening = MAIA_bodlis,
    MAIA_Trusting = MAIA_trust, MAIA_EmoAwareness = MAIA_emoaw,
    ICQ = ICQ_sum,
    STAIT_Sum = STAIT_sum,
    TAS_DIF = TAS_ident, TAS_EOT = TAS_ext, TAS_DDF = TAS_des,
    BPQ_BodyAwareness = BPQ_sum
  ) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5), range = c(0, 6)))) # Original scale 0-6
```

@@

```{r}
df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation,
  ) |>
  filter(!is.na(Urinate)) |> 
  datawizard::rescale(select=ias_vars, to = c(0, 5), range = c(0, 1)) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5)))) 
```

@@

df13$PHQ4_Depression <- (df13$PHQ4_Depression_4 + df13$PHQ4_Depression_3)/2
df13$PHQ4_Anxiety <- (df13$PHQ4_Anxiety_2 + df13$PHQ4_Anxiety_1)/2

@@

df16 <- read.csv("../data/Scharte2025/data_IAS_rs.csv") |>
  rename(Age= age, Gender = gender_identity, Education = education,
         Heart = ias1, Hungry = ias2, Breathing = ias3, Thirsty = ias4, Urinate = ias5, 
         Defecate=ias6, Taste = ias7,Vomit = ias8, Sneeze = ias9, Cough = ias10, 
         Temp = ias11, Sex_arousal = ias12, Wind = ias13, Burp = ias14,Muscles = ias15, 
         Bruise = ias16, Pain = ias17, Blood_Sugar = ias18, Affective_touch = ias19, 
         Tickle =ias20, Itch = ias21,
         ) |>
  mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 4, 5) ~ "Other",
    Gender == 6 ~ "NA"),
    Education = case_when(
      Education == 6 ~ "Bachelor",
      Education == 7 ~ "Master",
      Education == 8 ~ "Doctorate",
      Education == 2 | Education == 3 ~ "High School", # GCSE + A-levels (16-18 years old)
      Education == 4 | Education == 5 ~ "Other",       # NVQ and foundation year
      Education == 1 ~ "No education"),
    MAIA_Noticing = (maia1 + maia2 + maia3 + maia4)/4,
    MAIA_NotDistracting = (maia5_rev + maia6_rev + maia7_rev +maia8_rev + maia9_rev + maia10_rev)/6, 
    MAIA_NotWorrying = (maia11_rev +maia12_rev  + maia13)/3,
    MAIA_AttentionReg = (maia16 + maia17 + maia18 + maia19 + maia20 + maia21 + maia22)/7,
    MAIA_EmoAwareness = (maia23 + maia24 + maia25 + maia26 +maia27)/5,
    MAIA_SelfReg = (maia28 + maia29 + maia30 + maia31)/4,
    MAIA_BodyListening = (maia32 + maia33 +maia34)/3,
    MAIA_Trusting = (maia35 + maia36 + maia37)/3 ,
    GAD7_Sum = rowSums(across(starts_with("gad1_")), na.rm = TRUE),
    PHQ9_Sum = rowSums(across(starts_with("phq1_")), na.rm = TRUE)) |>
  filter (!Age == 2004.00, !Age == 1999.00, # misreported age
          att == 2) # only those that select 'no' the attention check

### 2025-08-13 analysis/study2.qmd
changes rest of dimensions/ variable names

data <- rbind(
  data,
  # pool_coef(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
  # pool_coef(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
  )
```

@@

data <- rbind(
  data,
  #df2 
  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"),
  make_rez(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
  make_rez(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)"),

  make_rez(with = "TAS_des", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"), 
  make_rez(with = "TAS_ident", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "TAS_ext", component="Alexithymia", name = "External Thinking (TAS)"), 
  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"), 
  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  # make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (STAI-5)"),
  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-9)")
)
```

>>>>

data <- rbind(
  data,
  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
  )
```

@@

data <- rbind(
  data,
  #df2 
  make_rez(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)"),
  make_rez(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)"),
  make_rez(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)"),
  make_rez(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  make_rez(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  make_rez(with = "GAD2_Sum", component="Mood", name = "Anxiety (GAD-2)"), 
  make_rez(with = "STAIT_Sum", component="Mood", name = "Anxiety (STAI-T)"), 
  make_rez(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  make_rez(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
)
```
